---
title: "Final Project Group A"
output: html_notebook
---

# Member

-   Sae Nuruki

-   Saman Chekani Moghaddam

-   Samar Maghsoodi

-   Sidra Bushra

-   Koichiro Suzuki

# Analytical Objectives

-   Retrieving data regarding the wines which has made the most sales globally.

-   Which wine age is more popular with users based on rating.

-   Which harvest region produces the better wine and consequently higher price.

-   Brand names of each wine and their impact on wine price.

# Assumptions

1.  Lower ACD leads to a better wine and therefore higher price and popularity.

2.  Name of the wine irrespective of its quality is an important factor (more famous higher the price)

3.  Wines that are more aged up are costlier compared to ones that are harvested more recently

4.  Higher ratings predominantly means the higher price of each wine.

5.  Lowers rsg often means higher price

6.  Number of testers and alcohol level does not have a significant effect on pricing

7.  BD does not have a noticeable effect on pricing

# Preparation

```{r}
library(ggplot2);
```

# Data Import

```{r}
BurgundySip <- read.csv("~/Documents/DataAnalytics/Module2/Dataset/BurgundySip.csv", na.strings = c("", "NA", "N.V."));

yearRange <- range(BurgundySip$YR, na.rm = T);
BurgundySip$YR <- factor(BurgundySip$YR, 
                         levels = yearRange[1]:yearRange[2], 
                         ordered = T);
BurgundySip$REG <- as.factor(BurgundySip$REG);
BurgundySip$TP <- as.factor(BurgundySip$TP);
BurgundySip$RSG <- as.numeric(gsub(" ", "", BurgundySip$RSG));
BurgundySip$AL <- as.numeric(gsub(" ", "", BurgundySip$AL));
BurgundySip$DN <- as.numeric(gsub(" ", "", BurgundySip$DN));
```

# Data Understanding

## Check the structure

```{r}
str(BurgundySip);
```

## Check the summary

```{r}
summary(BurgundySip);
```

## Check the correlation

```{r}
BurgundySipNum <- sapply(BurgundySip[, !sapply(BurgundySip, is.character)], as.numeric);
heatmap(cor(na.omit(BurgundySipNum)));
```

# Treating Duplicates

SN is helpful to identify wines.

```{r}
sum(is.na(BurgundySip$SN)); # 47
```

There are 47 missing values and we need to fill the blank before starting treating duplicates values

## Step 1. Handle missing values of SN

SN is unique for each wines. And every observations which have same SN are duplicated with other variables excepting for RSG, AL and DN.

We remove the duplicated observations by SN. And fortunately there are only two SNs are missing.

```{r}
View(BurgundySip[is.na(BurgundySip$SN),]);
# We can found only 2 atomic observations are missing value of SN.
# Then we can fill the blank manually.
BurgundySip$SN[c(727, 730, 733)] <- BurgundySip$SN[c(726)];
BurgundySip$SN[2072:2115] <- BurgundySip$SN[c(2071)];
sum(is.na(BurgundySip$SN)); # 0
```

## Step 2. Aggregate RSG, AL and DN by SN

These 3 variables are slightly different by each duplicated observations. We can select every aggregate methods such as max(), min(), mean() and median().

We use the average for aggregating the records.

```{r}
RemovingDuplicated <- aggregate(cbind(RSG, AL, DN) ~ SN, 
                                data = BurgundySip, 
                                FUN = mean);
RemovingDuplicated$RSG <- round(RemovingDuplicated$RSG, 4);
RemovingDuplicated$AL <- round(RemovingDuplicated$AL, 4);
RemovingDuplicated$DN <- round(RemovingDuplicated$DN, 4);
```

## Step 3. Impute other variables with non-missing values

We want to merge other variables (excepting for SN, RSG, AL and DN) into the aggregated table. But by entering values appropriately, missing values can be efficiently removed.

We return the first non-NA value of the NAME column of Observations with the corresponding SN.

```{r}
for (rowIndex in 1:nrow(RemovingDuplicated)) {
  Duplicated_SN <- subset(BurgundySip, 
                          SN == RemovingDuplicated[rowIndex, "SN"]);
  RemovingDuplicated$NAME[rowIndex] <- Duplicated_SN[!is.na(Duplicated_SN$NAME), "NAME"][1];
  RemovingDuplicated$WINE[rowIndex] <- Duplicated_SN[!is.na(Duplicated_SN$WINE), "WINE"][1];
  RemovingDuplicated$YR[rowIndex] <- as.character(Duplicated_SN[!is.na(Duplicated_SN$YR), "YR"][1]);
  RemovingDuplicated$REG[rowIndex] <- as.character(Duplicated_SN[!is.na(Duplicated_SN$REG), "REG"][1]);
  RemovingDuplicated$TP[rowIndex] <- as.character(Duplicated_SN[!is.na(Duplicated_SN$TP), "TP"][1]);
  RemovingDuplicated$RT[rowIndex] <- Duplicated_SN[!is.na(Duplicated_SN$RT), "RT"][1];
  RemovingDuplicated$NUMR[rowIndex] <- Duplicated_SN[!is.na(Duplicated_SN$NUMR), "NUMR"][1];
  RemovingDuplicated$PR[rowIndex] <- Duplicated_SN[!is.na(Duplicated_SN$PR), "PR"][1];
  RemovingDuplicated$BD[rowIndex] <- Duplicated_SN[!is.na(Duplicated_SN$BD), "BD"][1];
  RemovingDuplicated$ACD[rowIndex] <- Duplicated_SN[!is.na(Duplicated_SN$ACD), "ACD"][1];
}
BurgundySip <- RemovingDuplicated;
BurgundySip$YR <- factor(BurgundySip$YR, 
                         levels = yearRange[1]:yearRange[2], 
                         ordered = T);
BurgundySip$REG <- as.factor(BurgundySip$REG);
BurgundySip$TP <- as.factor(BurgundySip$TP);
```

# Treating Outliers

A large NUMR does not yield a high RT average.

However, Wines with many testers should be weighted RT by NUMR to consider for their popularity compared to Wines with fewer testers.

```{r}
# Step1
# Convert NUMR into Z-score.
NUMR_Zscores <- (BurgundySip$NUMR - mean(BurgundySip$NUMR)) / sd(BurgundySip$NUMR);

# Step2 
# Adjust RT with the weight as new variable RT_WEI
BurgundySip$RT_WEI <- BurgundySip$RT + NUMR_Zscores / 100;
BurgundySip$RT_WEI <- ifelse(BurgundySip$RT_WEI > 5.0, 5.0, round(BurgundySip$RT_WEI, 2));

# Check how updates
plot(BurgundySip$NUMR, BurgundySip$RT, main = "Adjust RT as treating Outliers");
points(BurgundySip[BurgundySip$NUMR > 5000,]$NUMR, BurgundySip[BurgundySip$NUMR > 5000,]$RT_WEI, pch = 16, col = "magenta");
```

# Treating Missing Values

Let's check the missing values by column.

5 variables are still missing. We challenge these tasks by mainly 3 approaches.

```{r}
colSums(apply(BurgundySip, 2, FUN = is.na));
#  SN  RSG   AL   DN NAME WINE   YR  REG   TP   RT NUMR   PR   BD  ACD RT_WEI 
#   0    0    0    0    0    0  144    0  151    0    0   56  433  433      0
# There are 5 variables which are still missing.
# YR: 144
# TP: 151
# PR: 56
# BD: 433
# ACD: 433
```

## YR: Year in which the grapes were harvested -- indicator of the AGE of the wine.

### Strategy

```{r}
# 1. Check the distribution
plot(BurgundySip$YR);
# 2. Check the correlation with other variables
cor(na.omit(BurgundySipNum))[,"YR"];
#        RSG          AL          DN          YR 
# 0.50752169 -0.32095274  0.25185578  1.00000000 
#        REG          TP          RT        NUMR 
#-0.15951649 -0.02402383 -0.54806420  0.05418860 
#         PR          BD         ACD 
#-0.42082790 -0.12789536  0.30873182 
# From the above result, we can find the moderate correlation variables, RSG, RT and PR
ggplot(BurgundySip, aes(round(RSG, 1), YR)) + 
  geom_point() + 
  geom_smooth(method = "lm", col = "red") + 
  geom_smooth(method = "loess", col = "blue") + 
  geom_smooth(col = "green");


meanYear_RSG <- aggregate(as.integer(as.character(YR)) ~ round(RSG, 1), BurgundySip, FUN = mean);
names(meanYear_RSG) <- c("RSG", "YR");
plot(meanYear_RSG$RSG, meanYear_RSG$YR);
ggplot(meanYear_RSG, aes(RSG, YR)) + 
  geom_point() + 
  geom_smooth(method = "lm", col = "red") + 
  geom_smooth(method = "loess", col = "blue") + 
  geom_smooth(method = "gam", col = "orange") + 
  geom_smooth(method = "glm", col = "green");
# Please look at the graph. It displays the beautiful quadratic curve.
# We can predict the year with RSG.
```

### Step 1. Regression Model Based

Nonlinear Regression suite with this task.

```{r}
yearPredictModel <- loess(YR ~ RSG, data = meanYear_RSG);
summary(yearPredictModel);
# loess(formula = YR ~ RSG, data = meanYear_RSG)
# Number of Observations: 82 
# Equivalent Number of Parameters: 4.85 
# Residual Standard Error: 6.682 
# Trace of smoother matrix: 5.31  (exact)

missingYR_RSG <- BurgundySip$RSG[is.na(BurgundySip$YR)];
predictYR <- predict(yearPredictModel, missingYR_RSG);
missingYR_RSG[which(is.na(predictYR))]; # 15.9014: This value is out of range 
predictYR[is.na(predictYR)] <- 2021;
BurgundySip$YR[is.na(BurgundySip$YR)] <- round(predictYR, 0);
```

## PR: Price in euros [€]

### Strategy

```{r}
# 1. Check the distribution
plot(BurgundySip$PR);
# 2. Check the correlation with other variables
cor(na.omit(BurgundySipNum))[,"PR"];
#         YR         REG          TP          RT 
#-0.41471733  0.06908034  0.02867421  0.64897778 
#       NUMR          PR          BD         ACD 
#-0.04091818  1.00000000  0.14725705 -0.04174460 
#        RSG          AL          DN 
#-0.52882810  0.34152337 -0.25518207 
# From the above result, we can find the moderate correlation variables, YR, RT and RSG
plot(round(BurgundySip$RSG, 1), log(BurgundySip$PR));
ggplot(BurgundySip, aes(round(RSG, 1), log(PR))) + 
  geom_point() + 
  geom_smooth(method = "lm", col = "red") + 
  geom_smooth(method = "loess", col = "blue") + 
  geom_smooth(col = "green");
# Please look at the graph. It displays the beautiful straight line.
# We can predict the price with RSG.
```

### Step 1. Regression Model Based

Linear Regression suite with this task.

```{r}
train_index <- !is.na(BurgundySip$PR) & BurgundySip$RSG < 10;
train_RSG <- round(BurgundySip$RSG[train_index], 1);
train_PR <- BurgundySip$PR[train_index];
pricePredictModel <- lm(log(train_PR) ~ train_RSG);
coefficients(pricePredictModel);
# (Intercept)   train_RSG 
#  10.4689374  -0.7572643 

test_RSG <- BurgundySip$RSG[is.na(BurgundySip$PR)];
predictPR <- exp(1)^(-0.7572643 * test_RSG + 10.4689374);
BurgundySip$PR[is.na(BurgundySip$PR)] <- round(predictPR, 0);
```

## TP: Wine variety

### Strategy

```{r}
# 1. Check the distribution
plot(BurgundySip$TP);
# 2. Check the correlation with other variables
cor(na.omit(BurgundySipNum))[,"TP"];
#        RSG          AL          DN          YR 
#-0.16671515  0.06265274 -0.03792722 -0.02402383 
#        REG          TP          RT        NUMR 
# 0.50523265  1.00000000  0.12509236  0.03436571 
#         PR          BD         ACD 
# 0.03020858  0.47570761 -0.11705663 
# From the above result, we can find the moderate correlation variables, REG and BD.
# There are so many missing values in BD, then filling TP with REG might be good solution.
heatmap(table(BurgundySip$TP, BurgundySip$REG));
TP_REG <- table(BurgundySip$TP, BurgundySip$REG);
```

### Step.1 Year is different, but the name of wine is same

We can fill the missing value by referring other same name wines.

```{r}
naTP_BurgundySip <- BurgundySip[is.na(BurgundySip$TP), ];
for (rowIndex in 1:nrow(naTP_BurgundySip)) {
  Duplicated_WINE <- subset(BurgundySip, WINE == naTP_BurgundySip$WINE[rowIndex]);
  naTP_BurgundySip$TP[rowIndex] <- Duplicated_WINE$TP[!is.na(Duplicated_WINE$TP)][1];
}
BurgundySip$TP[is.na(BurgundySip$TP)] <- naTP_BurgundySip$TP;
```

### Step.2 Remove Minor wines

Minor wines don't have enough information and they don't affect our analytics results.

```{r}
naTP_BurgundySip <- BurgundySip[is.na(BurgundySip$TP), ];
existTP_BurgundySip <- BurgundySip[!is.na(BurgundySip$TP), ];

BurgundySip_with1 <- cbind(BurgundySip, 1);
names(BurgundySip_with1)[length(names(BurgundySip_with1))] <- "Count";
countREG <- aggregate(Count ~ REG, BurgundySip_with1, FUN = sum);
minorWines <- subset(countREG, Count <= 3);
naTP_BurgundySip <- naTP_BurgundySip[!(naTP_BurgundySip$REG %in% minorWines$REG), ];
BurgundySip <- rbind(existTP_BurgundySip, naTP_BurgundySip);
```

### Step.3 Research each type of wine manually

We recognize that these wines which missing the TP are different type of others.

Some of them are new types (such as "Rose", "Dessert", "Fortified" and "Sparkling").

We want to save these precious wines for analysis and decide to get the major type of wine on web.

We assume Major category of wine ("Red", "White", "Rose", "Sparkling" and so on) behave similar with original TP.

We challenge to fill the missing values by researching.

```{r}
naTP_BurgundySip <- BurgundySip[is.na(BurgundySip$TP), ];
length(naTP_BurgundySip[!duplicated(naTP_BurgundySip$WINE),]$WINE); # 68
levels(BurgundySip$TP) <- c(levels(BurgundySip$TP), "White", "Rose", "Dessert", "Fortified");

BurgundySip$TP[BurgundySip$WINE == "Treixadura"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Tintilla de Rota"] <- "Red";
BurgundySip$TP[BurgundySip$WINE == "Reserva Vermouth Rojo"] <- "Red";
BurgundySip$TP[BurgundySip$WINE == "Pla dels Angels Rosado"] <- "Rose";
BurgundySip$TP[BurgundySip$WINE == "Pedra de Guix"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Massipa de Scala Dei Garnatxa Blanca - Xenin"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Cepas Vellas Godello"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Salvaxe"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Le Domaine Blanco de Guarda"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Malvasia"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "No. 2 Victoria"] <- "Dessert";
BurgundySip$TP[BurgundySip$WINE == "Le Rose"] <- "Sparkling";
BurgundySip$TP[BurgundySip$WINE == "Tahulla Moscatel Blanco Seco"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Heaven & Hell"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Rosado de Larrainzar"] <- "Rose";
BurgundySip$TP[BurgundySip$WINE == "Nun Vinya dels Taus"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Ekam Essencia"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Fino La Barajuela"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "O Luar do Sil Valdeorras Godello Sobre Lias"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "San Valentin Parellada"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Nounat"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Blanco"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Dolc Mataro"] <- "Dessert";
BurgundySip$TP[BurgundySip$WINE == "La Chispa Negra"] <- "Dessert";
BurgundySip$TP[BurgundySip$WINE == "Godello Blanco"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Gran Reserva Rosado"] <- "Rose";
BurgundySip$TP[BurgundySip$WINE == "Manar dos Seixas"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Muscat"] <- "Sparkling";
BurgundySip$TP[BurgundySip$WINE == "Stairway To Heaven Rosado"] <- "Rose";
BurgundySip$TP[BurgundySip$WINE == "Godello"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Gessami"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "200 Cestos Godello"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Ekam"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "A Pita Cega"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Recondita Armonia Monastrell Dulce"] <- "Dessert";
BurgundySip$TP[BurgundySip$WINE == "Finca Misenhora Edicion Limitada"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Dolc de L'Obac"] <- "Dessert";
BurgundySip$TP[BurgundySip$WINE == "As Sortes Val do Bibei Godello"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Vinyes Altes de Les Garrigues Vi Blanc"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Gran Barquero Palo Cortado Solera 25 Anos"] <- "Fortified";
BurgundySip$TP[BurgundySip$WINE == "Sorte O Soro Val do Bibei"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Fondillon Gran Reserva"] <- "Dessert";
BurgundySip$TP[BurgundySip$WINE == "Penalba Lopez Blanco"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "El Cuentista"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Adega do Moucho Treixadura"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Vermello Vermu"] <- "Fortified";
BurgundySip$TP[BurgundySip$WINE == "Nelin Priorat"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Vendimia Tardia Moscatel"] <- "Dessert";
BurgundySip$TP[BurgundySip$WINE == "Gratallops Escanya-Vella"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "La Revelia Godello"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Branco Vermu"] <- "Fortified";
BurgundySip$TP[BurgundySip$WINE == "Vi De Glass Gewurztraminer"] <- "Dessert";
BurgundySip$TP[BurgundySip$WINE == "Molino Real"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Porcellanic VI Xarel-lo Sur Lie"] <- "Dessert";
BurgundySip$TP[BurgundySip$WINE == "Navarra Vendimia Tardia Coleccion 125"] <- "Dessert";
BurgundySip$TP[BurgundySip$WINE == "El Rocallis"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Vino de Autor Ribeiro Blanco"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "La Solana Alta"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "La Silleria"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Casta Diva Cosecha Miel Moscatel Dulce"] <- "Dessert";
BurgundySip$TP[BurgundySip$WINE == "Selma de Nin Blanco"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Selection 1884 Vermouth Gran Reserva"] <- "Fortified";
BurgundySip$TP[BurgundySip$WINE == "Vallegarcia Viognier"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Louro Godello"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Diables"] <- "Rose";
BurgundySip$TP[BurgundySip$WINE == "V Dulce de Invierno"] <- "Dessert";
BurgundySip$TP[BurgundySip$WINE == "Atlantico"] <- "White";
BurgundySip$TP[BurgundySip$WINE == "Vina de Martin Escolma Ribeiro"] <- "White";
```

## BD: Body score, defined as the richness and weight of the wine in your mouth [from 1-5]

### Strategy

```{r}
# 1. Check the distribution
table(BurgundySip$BD);
#   2    3    4    5 
#  34  380 1874  884 
# 2. Check the correlation with other variables
cor(na.omit(BurgundySipNum))[,"BD"];
#        RSG          AL          DN
#-0.31985032  0.14935454 -0.10624900 
#         YR         REG          TP          RT 
#-0.12789536  0.47001416  0.47570761  0.30123444 
#       NUMR          PR          BD         ACD 
# 0.09674641  0.17308001  1.00000000 -0.07718933 
```

### Step.1

From the above result, we can find the moderate correlation variables, RSG, REG and TP.

And especially the following table explain the perfect relationship.

BD and TP have a M to 1 relationship.

```{r}
table(BurgundySip$BD, BurgundySip$TP);
bdTPTable <- aggregate(BD ~ TP, BurgundySip, FUN = mean);
missingBD_BurgundySip <- BurgundySip[is.na(BurgundySip$BD),];
existingBD_BurgundySip <- BurgundySip[!is.na(BurgundySip$BD),];
removeBDIndexes <- !(names(BurgundySip) == "BD");
missingBD_BurgundySip <- merge(missingBD_BurgundySip[removeBDIndexes], bdTPTable, by = "TP", all.x = T);
BurgundySip <- rbind(existingBD_BurgundySip, missingBD_BurgundySip);
```

### Step.2

Treat New TP (White, Rose, Dessert, Fortified)

Solve this task by Multiple Linear Regression Models

```{r}
missingBD_BurgundySip <- BurgundySip[is.na(BurgundySip$BD),];
existingBD_BurgundySip <- BurgundySip[!is.na(BurgundySip$BD),];
bdPredictModel <- lm(BD ~ RSG + AL + YR, data = existingBD_BurgundySip);
missingBD_BurgundySip$BD <- predict(bdPredictModel, missingBD_BurgundySip);
missingBD_BurgundySip$BD <- round(missingBD_BurgundySip$BD, 0);
BurgundySip <- rbind(existingBD_BurgundySip, missingBD_BurgundySip);
```

## ACD: Acidity score, defined as wine's "pucker" or tartness; it's what makes a wine refreshing and your tongue salivate and want another sip [from 1-5]

### Strategy

```{r}
# 1. Check the distribution
table(BurgundySip$ACD);
#   1    2    3 
#  34   67 3071 
# 2. Check the correlation with other variables
cor(na.omit(BurgundySipNum))[,"ACD"];
#         RSG           AL           DN           YR 
# 0.131538949 -0.085149122  0.077349454  0.308731823 
#         REG           TP           RT         NUMR 
# 0.005073087 -0.117056631 -0.125947492  0.066169986 
#          PR           BD          ACD 
#-0.056487009 -0.077189335  1.000000000 
```

### Step.1

From the above result, we can find the moderate and weak correlation variables, YR, TP and RT.

And especially the following table explain the perfect relationship.

ACD and TP have a M to 1 relationship.

```{r}
table(BurgundySip$ACD, BurgundySip$TP);
acdTPTable <- aggregate(ACD ~ TP, BurgundySip, FUN = mean);
missingACD_BurgundySip <- BurgundySip[is.na(BurgundySip$ACD),];
existingACD_BurgundySip <- BurgundySip[!is.na(BurgundySip$ACD),];
removeACDIndexes <- !(names(BurgundySip) == "ACD");
missingACD_BurgundySip <- merge(missingACD_BurgundySip[removeACDIndexes], acdTPTable, by = "TP", all.x = T);
BurgundySip <- rbind(existingACD_BurgundySip, missingACD_BurgundySip);
```

### Step.2

Treat New TP (White, Rose, Dessert, Fortified)

Solve this task by Multiple Linear Regression Models

```{r}
missingACD_BurgundySip <- BurgundySip[is.na(BurgundySip$ACD),];
existingACD_BurgundySip <- BurgundySip[!is.na(BurgundySip$ACD),];
acdPredictModel <- lm(ACD ~ RSG + YR, data = existingACD_BurgundySip);
missingACD_BurgundySip$ACD <- predict(acdPredictModel, missingACD_BurgundySip);
missingACD_BurgundySip$ACD <- round(missingACD_BurgundySip$ACD, 0);
BurgundySip <- rbind(existingACD_BurgundySip, missingACD_BurgundySip);
```

# Check the result of cleaning process

```{r}
# We treat every missing values properly.
colSums(apply(BurgundySip, 2, FUN = is.na));
#  SN  RSG   AL   DN NAME WINE   YR  REG   TP   RT NUMR   PR   BD  ACD RT_WEI 
#   0    0    0    0    0    0    0    0    0    0    0    0    0    0      0
```

# Descriptive Analysis and Findings

Data Summarization, Visualization, Statistical Analysis, and Calculations

a.  Describe how the calculations were performed and why they had to be performed.

b.  Describe the use of visual artifacts in the analysis.

c.  Explain the findings.

## The exploratory analysis :

1.  Which particular range of age (YR) in regard to wines had the highest price?

2.  Determine the rating range pertaining to the wines which had the highest price.

3.  What is the average price of wines based on the region which the grapes are originated from ?

4.  Calculate the average price of wines based on the name of the aforementioned beverages

5.  The average price of the wines based on the ratings pertinent to each brand.

```{r}
# 1.Which particular range of age (YR) in regard to wines had the highest price?
plot(BurgundySip$YR, BurgundySip$PR);
aggregate(PR ~ YR, data = BurgundySip, FUN = mean);
plot(aggregate(PR ~ YR, data = BurgundySip, FUN = mean));

# 2.Determine the rating range pertaining to the wines which had the highest price.
aggregate(PR ~ round(RT, 1), data = BurgundySip, FUN = mean);
plot(aggregate(PR ~ round(RT, 1), data = BurgundySip, FUN = mean));

# 3.What is the average price of wines based on the region which the grapes are originated from ?
aggregate(PR ~ REG, data = BurgundySip, FUN = mean);
plot(aggregate(PR ~ REG, data = BurgundySip, FUN = mean));

# 4.Calculate the average price of wines based on the name of the aforementioned beverages
aggregate(PR ~ NAME, data = BurgundySip , FUN = mean);
plot(aggregate(PR ~ NAME, data = BurgundySip , FUN = mean));

# 5.The average price of the wines based on the ratings pertinent to each brand.
aggregate(PR ~ RT, data = BurgundySip , FUN = mean);
plot(aggregate(PR ~ RT, data = BurgundySip , FUN = mean));
```

# Predictive Analysis and Findings

## Generate the Multiple Linear Regression Model

To predict price based on region and rating RT

```{r}
BurgundySipLM <- lm(PR~RT+REG, data=BurgundySip);
BurgundySipLM;

summary(BurgundySipLM);

trainIndex <- sample(nrow(BurgundySip), 0.8 * nrow(BurgundySip));
BurgundySip_train <- BurgundySip[trainIndex, ];
BurgundySip_test <- BurgundySip[-trainIndex, ];
```

```{r}
BurgundySip_LM<- lm(PR~RSG + RT,data=BurgundySip_train);
BurgundySip_LM;


predictPR <- predict(BurgundySip_LM, BurgundySip_test);
plot(BurgundySip_test$PR, predictPR);
cor(BurgundySip_test$PR, predictPR);
```

```{r}
BurgundySip_LM<- lm(PR~RSG + RT,data=BurgundySip_train);
BurgundySip_LM;#Residual standard error is 128.7

predictPR <- predict(BurgundySip_LM, BurgundySip_test);
plot(BurgundySip_test$PR, predictPR);
cor(BurgundySip_test$PR, predictPR); #COr is 0.5333124
naIndex <- is.na(predictPR); 
cor(BurgundySip_test$PR[!naIndex], predictPR[!naIndex]);#COR is 0.5333124
```

## Generate the Multiple Non-Linear Regression Model

To predict price based on RSG and rating RT

```{r}
BurgundySip_NLM<- loess(PR~RSG + RT,data=BurgundySip);
BurgundySip_NLM;
summary(BurgundySip_NLM);#Residual standard Error is 92

trainIndex <- sample(nrow(BurgundySip), 0.8 * nrow(BurgundySip));
BurgundySip_train <- BurgundySip[trainIndex, ];
BurgundySip_test <- BurgundySip[-trainIndex, ];
```

```{r}
BurgundySip_NLM<- loess(PR~RSG + RT,data=BurgundySip_train);
BurgundySip_NLM;#Residual standard error is 81.62


predictPR <- predict(BurgundySip_NLM, BurgundySip_test);
plot(BurgundySip_test$PR, predictPR);
cor(BurgundySip_test$PR, predictPR);
```

```{r}
BurgundySip_NLM<- loess(PR~RSG + RT,data=BurgundySip_train);
BurgundySip_NLM;#Residual standard error is 81.62

predictPR <- predict(BurgundySip_NLM, BurgundySip_test);
plot(BurgundySip_test$PR, predictPR);
cor(BurgundySip_test$PR, predictPR);
naIndex <- is.na(predictPR);
cor(BurgundySip_test$PR[!naIndex], predictPR[!naIndex]);
```

# Cluster-based Analysis and Findings

## Goal

We aim to discover the wines which can be sold at higher unit prices by grouping the wines based on potential relationships.

We achieve these 3 analytical objectives with cluster methods.

1.  Retrieving data regarding the wines which has made the most sales globally.

2.  Which harvest region produces the better wine and consequently higher price.

3.  Brand names of each wine and their impact on wine price.

## Topics

We design Clustering tasks that is meaningful in all Variables except for PR and RT, since they are the target of the evaluation.

According to our global Analytical Objectives, two types of analytical objectives are hypothesized.

### Investigate potential groupings based on taste of Wine, independent of Brand and price, to see if it has an impact on TP and PR.

Wine taste means the sweetness, acidity, and richness that customers experience when they actually taste the wine.

The following five Variables categorize the feeling that customers have when they drink Wine without both the brand and the price. We reveal the potential tastes that our customer prefer.

• BD: Body score, defined as the richness and weight of the wine in your mouth [from 1-5]

• ACD: Acidity score, defined as wine's "pucker" or tartness; it's what makes a wine refreshing and your tongue salivate and want another sip [from 1-5]

• RSG: residual sugar level of the wine [from 0 -16]

• AL: Alcohol percentage of the wine.

• DN: The typical density or specific gravity of the wine is generally between 1.080 and 1.090.

### Investigate potential groupings based on Brand and harvest region of Wine, independent of taste and price, to see if there is an impact on TP and PR.

It generally says that Wine is greatly influenced by brands in terms of price and popularity.

Without using taste and price of Wine, we categorize based on brands to identify the impact of price and popularity.

We hypothesized that the TP and REG in the BurgundySip dataset would be useful in explaining Brand in Wine.

• REG: Region of the wine

• TP: Wine variety

## Preparation

To visualize the cluster classification in this analysis and make it easier to compare visually, we will use ggplot2.

```{r}
library(ggplot2);

BurgundySip$YR_Num <- as.integer(BurgundySip$YR);
BurgundySip$REG_Num <- as.integer(BurgundySip$REG);
BurgundySip$TP_Num <- as.integer(BurgundySip$TP);
```

## Cluster by Taste

Select a model that can be optimally classified by the 5 Variables that are components of Wine Taste.

Of these five factors, ACD and BD are excluded from the clustering because they do not make a significant difference.

```{r}
fit <- kmeans(BurgundySip[, c("RSG", "AL", "DN")], 5);
BurgundySip$TasteCL <- as.factor(fit$cluster);

# visualization
## 1
ggplot(BurgundySip, aes(x = DN, bg = TasteCL)) + 
     geom_bar(position = "fill") +
     labs(title = "DN by TasteCL");
## 2
ggplot(BurgundySip, aes(x = RSG, bg = TasteCL)) + 
  geom_histogram() +
  labs(title = "RSG by TasteCL");
## 3
ggplot(BurgundySip, aes(x = PR, y = RT, col = TasteCL)) + 
  geom_point() +
  labs(title = "PR x RT by TasteCL");
## 4
ggplot(BurgundySip, aes(x = TP_Num, bg = TasteCL)) + 
  geom_bar(position = "fill") +
  labs(title = "TP by TasteCL");
```

## Cluster by Brand

Since both REG and TP are factors, convert them to numbers so that they can be used in kmean().

If we simply do as.integer(BurgundySip\$REG), regions that happen to be close in order of REG level will be recognized as highly similar to each other.

One-Hot Encoding method is a method to convert ML input data of common factors.

However, in this case, One-Hot Encoding of REG and TP makes it difficult to obtain each other's features, so we design a column where the REG distribution vector is created for each TP.

```{r}
# Step 1. Create a relationship matrix between REG and TP.
REG_TP_Matrix <- table(BurgundySip$REG, BurgundySip$TP);
heatmap(REG_TP_Matrix);

# Step 2. Convert REG distribution vector by TP to DataFrame.
columnNams_TP <- paste0("TP_", gsub(" ", "", colnames(REG_TP_Matrix)));
REG_TP_DataFrame <- data.frame(REG = rownames(REG_TP_Matrix));
for (col in 1:ncol(REG_TP_Matrix)) {
  REG_TP_DataFrame[, ncol(REG_TP_DataFrame) + 1] <- as.integer(REG_TP_Matrix[, col] > 0);
  colnames(REG_TP_DataFrame)[ncol(REG_TP_DataFrame)] <- columnNams_TP[col];
}
# Step 3. LeftJoin a REG distribution vector by TP to create a data frame of type Numeric
BurgundySip <- merge(BurgundySip, REG_TP_DataFrame, by = "REG", all.x = T);

fit <- kmeans(BurgundySip[, columnNams_TP], 10);
BurgundySip$BrandCL <- as.factor(fit$cluster);

# visualization
## 1
ggplot(BurgundySip, aes(x = REG, y = RT_WEI, col = BrandCL)) + 
  geom_point() +
  labs(title = "REG x RT_WEI by BrandCL");
## 2
ggplot(BurgundySip, aes(x = round(PR, -2), bg = BrandCL)) + 
  geom_bar(position = "fill") +
  labs(title = "PR by BrandCL");
## 3
ggplot(BurgundySip, aes(x = round(RSG), bg = BrandCL)) + 
  geom_bar(position = "fill") +
  labs(title = "RSG by BrandCL");
## 4
ggplot(BurgundySip, aes(x = BD, bg = BrandCL)) + 
  geom_bar(position = "fill") +
  labs(title = "BD by BrandCL");
```

## Conclusion

```{r}
BurgundySip_Conclusion <- aggregate(cbind(PR, RT_WEI) ~ TasteCL + BrandCL, data = BurgundySip, FUN = mean);
BurgundySip_Conclusion <- BurgundySip_Conclusion[order(BurgundySip_Conclusion$RT_WEI, decreasing = T),];
View(BurgundySip_Conclusion);
```
